Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2025-07-09 analysis/paper/article.qmd
read from local versions of the wiki pages

# download the wiki pages so we can have them locally, in case they get deleted or heavily modified
walk(
urls_for_each_year[1:9],
~.x %>%
  read_html() %>% 
  xml2::write_xml(., paste0("analysis/data/raw_data/", basename(.x), ".html")))

@@

@@

# get the data
# 2021-22 and 2022-2023
current_user_tbl <-
map(
urls_for_each_year[1:9],
~.x %>%
  read_html() %>%
  html_elements("p+ table td") %>%
  html_text2()
)

current_user_tbl_2021_22 <-
    urls_for_each_year[10]  %>%
      read_html() %>%
      html_elements("table:nth-child(1086) td") %>%
      html_text2()

current_user_tbl_2022_2023 <-
    urls_for_each_year[11] %>%
      read_html() %>%
      html_elements("h2+ .fandom-table td") %>%
      html_text2()

current_user_tbl_all <- append(current_user_tbl,
                        c(list(current_user_tbl_2021_22),
                          list(current_user_tbl_2022_2023)
                        ))

>>>>

# download the wiki pages so we can have them locally, in case they get deleted or heavily modified
walk(
urls_for_each_year,
~.x %>%
  read_html() %>% 
  xml2::write_xml(., paste0("analysis/data/raw_data/", basename(.x), ".html")))

@@

```{r}
# get the data from our local versions of the pages
# 2021-22 and 2022-2023
current_user_tbl <-
map(
paste0(here("analysis/data/raw_data/"), 
       basename(urls_for_each_year)[1:9],
       ".html"),
~.x %>%
  read_html() %>%
  html_elements("p+ table td") %>%
  html_text2()
)

current_user_tbl_2021_22 <-
    paste0(here("analysis/data/raw_data/"), 
       basename(urls_for_each_year)[10],
       ".html")  %>%
      read_html() %>%
      html_elements("table:nth-child(1086) td") %>%
      html_text2()

current_user_tbl_2022_2023 <-
   paste0(here("analysis/data/raw_data/"), 
       basename(urls_for_each_year)[11],
       ".html") %>%
      read_html() %>%
      html_elements("h2+ .fandom-table td") %>%
      html_text2()

current_user_tbl_all <- append(current_user_tbl,
                        c(list(current_user_tbl_2021_22),
                          list(current_user_tbl_2022_2023)
                        ))
```

@@
